---
title: "How to modify Plot Legend in ggplot2"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
---
# Part 1 - Set-up
We firstly start with a original graph.
```{r}
library(ggplot2)
library(readxl)
wcgs<-readxl::read_xls("wcgs.xls")
gp<-ggplot(data=wcgs,aes(x=behpat,y=height,fill=behpat))+geom_boxplot()
gp
```

# Part 2 - Removing the legend
You can remove all the legends in a graph, using theme().
```{r}
#Remove all the legend
gp+theme(legend.position = "none")
```

# Part 3 - Order of Items in the Legend

## Changing the order of items in the legend
This changes the order of items to B3,B4,A1,A2.

```{r}
gp+scale_fill_discrete(breaks=c("B3", "B4","A1", "A2"))
```

## Reversing the order of items in the legend
You can use scale_fill_discrete to reverse the legend order
```{r}
gp+scale_fill_discrete(guide=guide_legend(reverse=TRUE))
```

# Part 4 - Legend Title and Labels

## Hiding the legend title
You can use theme() to hide the legend title.
```{r}
gp+theme(legend.title = element_blank())
```

## Modifying the appearance of legend title
You can use theme() to modify the appearance of legend title.
```{r}
gp + theme(legend.title = element_text(colour="red", size=10, face="bold"))
```

## Modifying the appearance of legend labels
You can use theme() to modify the appearance of legend labels.
```{r}
gp + theme(legend.text = element_text(colour="red", size = 8, face = "bold"))
```

# Part 5 - Legend Box

## Modifying the legend box
The default setting of legend will not have a box. You can add a box and modify its properties.
```{r}
gp + theme(legend.background = element_rect(fill="gray90", size=.5, linetype="dotted"))
```

# Part 6 - Legend Position
## Changing the position of the legend
You can postion legend in different area of outside the plot by theme(). (left/right/top/bottom)
```{r}
gp + theme(legend.position="top")
```
